Metal Enrichment and Stellar Populations of High Redshift Dwarf Galaxies

### 2011-01-14 ms.tex
Changing to MNRAS formatting.

%\documentclass[apjl]{emulateapj}
\documentclass[12pt,preprint]{aastex}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage[section] {placeins}
\bibliographystyle{apj}
\citestyle{apj}

@@

\input macros.tex

@@

\shorttitle{High Redshift Dwarf Galaxies}
\shortauthors{WISE ET AL.}

\title{Metal Enrichment and Stellar Populations of High Redshift Dwarf
  Galaxies}

\author{John H. Wise\altaffilmark{1,2}, 
  Matthew J. Turk\altaffilmark{3},
  Michael L. Norman\altaffilmark{3},
  Tom Abel\altaffilmark{4}}

\altaffiltext{1}{Department of Astrophysical Sciences, Princeton
  University, Peyton Hall, Ivy Lane, Princeton, NJ 08544}
\altaffiltext{2}{Hubble Fellow}
\altaffiltext{3}{Center for Astrophysics and Space Sciences,
  University of California at San Diego, La Jolla, CA 92093}
\altaffiltext{4}{Kavli Institute for Particle Astrophysics and
  Cosmology, Stanford University, Menlo Park, CA 94025}
\email{jwise@astro.princeton.edu}

@@

\keywords{cosmology --- methods: numerical --- hydrodynamics ---
  radiative transfer --- star formation}

@@

\acknowledgments

@@

%\clearpage
%\input biblio.tex
\bibliography{ms}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}

\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage[section] {placeins}
\bibliographystyle{mn2e}
\citestyle{mn2e}

@@

\input macros.tex
\voffset=-1.4cm

@@

\title[High Redshift Dwarf Galaxies]{Metal Enrichment and Stellar
  Populations of High Redshift Dwarf Galaxies}

\author[Wise et al.]{John H. Wise$^1$\thanks{Hubble Fellow; e-mail:
    jwise@astro.princeton.edu}, Matthew J. Turk$^2$, Michael
  L. Norman$^2$, Tom Abel$^3$\\
  $^{1}$ Department of Astrophysical Sciences, Princeton University,
  Peyton Hall, Ivy Lane, Princeton, NJ 08544, USA\\
  $^{2}$ Center for Astrophysics and Space Sciences,
    University of California at San Diego, La Jolla, CA 92093, USA\\
  $^{3}$ Kavli Institute for Particle Astrophysics and Cosmology,
  Stanford University, Menlo Park, CA 94025, USA}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2010}

\maketitle
\label{firstpage}

@@

\begin{keywords}
  cosmology --- methods: numerical --- hydrodynamics ---
  radiative transfer --- star formation
\end{keywords}

@@

\section*{Acknowledgements}

@@

\bibliography{ms}
\bsp
\label{lastpage}
